Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White Dwarf Progenitors

### 2019-02-09 paper/ms.tex
Even more on Carlyn's paper.

\begin{abstract}
The existence of "hybrid" white dwarfs, made of a C/O
core within a O/Ne shell is accepted, and studies indicate that these are 
viable progenitors for thermonuclear (type Ia) supernovae.
Recent work found that the C/O core is mixed with the surrounding O/Ne
while the white dwarf cools. To further investigate the efficacy
of these white dwarfs as progenitors of thermonuclear supernovae, we performed 
simulations of thermonuclear supernovae from a new series of hybrid progenitors
that include the effects of cooling. The progenitor white dwarf model
was constructed with the one-dimensional stellar evolution code MESA and
represented a star evolved through the phase of unstable interior mixing 
followed by accretion until it reached conditions for the ignition of 
carbon burning. This MESA model was then mapped to a two-dimensional initial 
condition and an explosion simulated with FLASH. For comparison, a similar
simulation of an explosion was performed from a traditional C/O progenitor
white dwarf. By comparing the yields of the explosions, we found that as
with earlier studies, these hybrid models are viable supernova progenitors.
We contrast explosions from these models with explosions 
from previous models {\color{red} without the mixing during the white dwarf cooling.}
\end{abstract}

@@

The simulations of supernova explosions presented here were performed
with a customized version of the Flash code, originally developed
at the University of Chicago.
Flash is a parallel, adaptive mesh, multi-physics simulation code
developed first for nuclear astrophysics applications and subsequently
for high-energy-density applications~\cite{Fryxetal00,calder.curtis.ea:high-performance,
calder.fryxell.ea:on,flash_pragmatic,flash_evolution}. 
Flash has been applied to a variety of astropysical problems by a host
of researchers, and the version we apply differs from other versions
principally in the modules describing thermonuclear burning via a 
flame capturing model.

@@

\subsection{Initial Conditions}

A hybrid white dwarf model constructed with the one-dimensional stellar 
evolution code MESA~\citep{mesa1,mesa2,mesa3,mesa3e} served as the 
initial conditions for the simulations of supernova explosions presented
in this work~\citep{brooksetal2017}.
The hybrid model was constructed to have conditions as similar a possible
to a ``classic" C/O model and the two shared the same central temperature
and density.  Figure~\ref{fig:init_conds} shows the density and temperature
profiles of the two initial one-dimensional models. 
\begin{figure}
\includegraphics[width=\columnwidth]{figures/initial_conds.png}
\caption{\label{fig:init_conds}
	We used MESA, a 1-D stellar evolution code, to create the hybrid model. We made the hybrid model have the same central temperature and density as the classic model. 
 We found that the most abundant isotopes in the model were C12, O16, Ne20. There were a few other isotopes that were added to form Ne22 later. We saw that  ….
Plotting the density verses solar radii, we found that the densest part of the star is in the center slowly decreasing until it hits 0 at the outer edge of the star. 
In order to see where we should ignite the flame, we plotted the temperature profile. It was found that the peak temperature is at the center of the star, therefore, it was obvious to ignite the flame in the core. (PUT IN TEMP PROFILE)
}
\end{figure}
In both models, and unlike the hybrid models of~\citet{willcoxetal2016}, the central
temperature was the highest at the center of the star and accordingly the simulations 
began with central initions.

\subsection{Created two-dimensional models from one-dimensional models}

The two-dimensional simulations were performed with a modified version
of the FLASH code developed at the University of Chicago. CITE
The initial one-dimensional MESA models were mapped to the two-dimensional 
FLASH grid. MORE HERE.

>>>>

\begin{abstract}
The existence of "hybrid" white dwarfs, made of a C/O
core within a O/Ne shell is accepted, and studies indicate that these are 
viable progenitors for thermonuclear (type Ia) supernovae.
Recent work found that the C/O core is mixed with the surrounding O/Ne
as the white dwarf cools prior to accretion, which results in lower central 
C fractions in the massive progenitor than previously assumed. To further 
investigate the efficacy of hybrid white dwarfs as progenitors of 
thermonuclear supernovae, we performed simulations of thermonuclear 
supernovae from a new series of hybrid progenitors that include the 
effects of cooling. The progenitor white dwarf model
was constructed with the one-dimensional stellar evolution code MESA and
represented a star evolved through the phase of unstable interior mixing 
followed by accretion until it reached conditions for the ignition of 
carbon burning. This MESA model was then mapped to a two-dimensional initial 
condition and an explosion simulated with FLASH. For comparison, a similar
simulation of an explosion was performed from a traditional C/O progenitor
white dwarf. By comparing the yields of the explosions, we found that as
with earlier studies, these hybrid models are viable supernova progenitors.
We contrast explosions from these models with explosions 
from previous hybrid models 
{\color{red} without the mixing during the white dwarf cooling}
and traditional C/O progenitors.
\end{abstract}

@@

The simulations of supernova explosions presented here were performed
with a customized version of the \FLASH code, originally developed
at the University of Chicago.
Flash is a parallel, adaptive mesh, multi-physics simulation code
developed first for nuclear astrophysics applications and subsequently
for high-energy-density applications~\cite{Fryxetal00,calder.curtis.ea:high-performance,
calder.fryxell.ea:on,flash_pragmatic,flash_evolution}. 
Flash has been applied to a variety of astropysical problems by a host
of researchers, and the version we apply differs from other versions
principally in the modules describing thermonuclear burning via a 
flame capturing model.

@@

\subsection{One-dimensional Hybrid Model}

The hybrid white dwarf model that served as the initial conditions 
for the simulations of supernova explosions presented in this work
was constructed with the one-dimensional stellar evolution code 
MESA~\citep{mesa1,mesa2,mesa3,mesa3e}. The evolution of the model 
included thermohalene mixing during the cooling phase and thus
had a lower C fraction than previous hybrid models~\citep{brooksetal2017}.
The hybrid model was constructed to have conditions as similar a possible
to a ``classic" C/O model and the two shared the same central temperature
and density.  Figure~\ref{fig:init_conds} shows the density and temperature
profiles of the two initial one-dimensional models. 
\begin{figure}
\includegraphics[width=\columnwidth]{figures/initial_conds.png}
\caption{\label{fig:init_conds}
Temperature, density, and  composition profiles of the one-dimensional hybrid 
progenitor WD. The central temperature and density were the same as
the tradtional C/O progenitor model. 
 We found that the most abundant isotopes in the model were C12, O16, Ne20. There were a few other isotopes that were added to form Ne22 later. We saw that  ….
Plotting the density verses solar radii, we found that the densest part of the star is in the center slowly decreasing until it hits 0 at the outer edge of the star. 
In order to see where we should ignite the flame, we plotted the temperature profile. It was found that the peak temperature is at the center of the star, therefore, it was obvious to ignite the flame in the core. (PUT IN TEMP PROFILE)
}
\end{figure}
In both models, and unlike the hybrid models of~\citet{willcoxetal2016}, the central
temperature was the highest at the center of the star and accordingly the simulations 
began with central initions.

\subsection{Ttwo-dimensional Models from One-dimensional Models}

The initial progenitor models for the two-dimensional simulations were
created from the one-dimensional \MESA models by mapping the one-dimensional
models onto the two-dimensional domain while 
preserving hydrostatic equilibrium.
As described above, the flame capturing scheme with progress
variables describing the evolution as the material burns. The \MESA
models, however, relied on a detailed reaction network that included
many species. Accordingly, the process of creating the two-dimensional
models for \FLASH required aggregating some of the species abundances.
As with much of this study, we applied the 
techniques of ~\citet{willcoxetal2016}.

The process of mapping the \MESA models began by converting 
the \MESA\ model to a uniform grid of $4$~km resolution. \MESA 
quantities in zones with spacing less than $4$~km 
were mass-weighted averaged and a quadratic interpolation
was used to calculate quantities for the case of \MESA zones having
a spacing greater than $4$~km. At this point, 
abundances of nuclides from the \MESA models were aggregated
into abundances of

representing neutron-rich metals were aggregated into

a variable representing
